Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-12 paper/latex/paper.tex
Redo commit 'changes from call'
Redo commit 'added abstract and changed title'
Redo commit 'Add to data gen section that samples are 4 secs'

\begin{figure*}
\includegraphics[scale=0.45]{CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure*}

@@

>>>>

\begin{figure}
\includegraphics[scale=0.45]{CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure}

@@

Although the data we trained the model on was fixed to four seconds of audio, the target samples can be of arbitrary length. By changing the mel hop length, which is the distance between the frames of the melspectrogram, an audio signal of any length can be represented as a matrix of the same size as the training data.

\subsection{Evaluation}
